---
title: "NVC Error Assessment"
author: "Melanie Kammerer"
date: "1/3/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Objective
The goal of this script is to summarize LANDFIRE assessment of NVC accuracy. LANDFIRE defines accuracy as agreement between vegetation class assigned to a 
field plot and the raster layer value at that location. For each lifeform (forest, shrub, herbaceous), the LANDFIRE team generated raster layers of vegetation (EVT and NVC) using CART methods with input layers of soils, topography, weather, and LANDSAT spectral indices (see [Zhu et al 2006](https://www.fs.fed.us/rm/pubs/rmrs_gtr175/rmrs_gtr175_197_215.pdf) for original method and [Picotte et al 2019](https://www.mdpi.com/2571-6255/2/2/35/htm) for ReMap methods).

```{r loadfiles}
library(dplyr); library(readxl)

toread <- list.files('./data/LANDFIRE_Accuracy/CSV_AccuracyData/', full.names = T)

for (i in toread) {
  region <- read.csv(i) %>%
    dplyr::mutate(Row.Total..pixels. = as.integer(Row.Total..pixels.),
                  Region = substr(basename(i), start=1, stop=2))
  
  if ('NVC.Map.Value' %in% names(region)) {
    region <- dplyr::mutate(region, NVC.Value = as.factor(NVC.Map.Value)) %>%
      dplyr::select(-NVC.Map.Value)
  }
  
    if ('NVC.Value' %in% names(region)) {
    region <- dplyr::mutate(region, NVC.Value = as.factor(NVC.Value))
  }
  
  if (i == toread[1]) {
    all <- region
  } else {
    all <- full_join(all, region)
  }
}

names(all) <- gsub(names(all), pattern=".", replacement = "_", fixed = T)

all <- dplyr::rename(all, Pct_Row_Pixels = X__of_Row_Pixels, Row_Total_Pixels= Row_Total__pixels_)
```

```{r readcdl}
for (year in 2012:2020) {
    
  if (year < 2018 & year != 2016) {
    files <- list.files(paste0('./data/CDL_Accuracy/CDL_', year, '_accuracy_assessments/CDL_', year,
    '_accuracy_assessments/'), full.names = T)
  } else if (year %in% c(2018, 2019, 2020)) {
      files <- list.files(paste0('./data/CDL_Accuracy/CDL_', year, '_accuracy_assessments/'), full.names = T)
  } else if (year == 2016) {
      files <- list.files(paste0('./data/CDL_Accuracy/CDL_', year, '_accuracy_assessments/CDL_', year,
    '_accuracy_assessments/buffered_validation/'), full.names = T)
  }
  
  files <- files[grepl(files, pattern='.xlsx')] # filter out non-excel files
  files <- files[!grepl(files, pattern='National')] # filter out national cdl results

  for (path in files) {
    
    # read correct sheet of excel file
    AL17_accuracy <- read_excel(path, sheet = "All - Matrix")
    
    # create column names for some that were blank
    names(AL17_accuracy) <- c('CDL_Name', 'CDL_Class', names(AL17_accuracy)[3:length(AL17_accuracy)])
    
    AL17_producer <- dplyr::filter(AL17_accuracy, CDL_Class %in% c('Producer', 'Omission', 'Kappa')) %>%
      dplyr::select(-CDL_Name, -CDL_Class, -Total, -User, -Commission, -Kappa) %>%
      t() %>%
      data.frame()
    names(AL17_producer) <- c('Producer', 'Omission', 'Kappa_Producer')
    
    # remove extra rows that are not data, add state and year columns from file name
    AL17_user <- dplyr::filter(AL17_accuracy, CDL_Class %in% 1:256) %>%
      dplyr::select(CDL_Name, CDL_Class, User, Commission, Kappa) %>%
      dplyr::rename(Kappa_User = Kappa)
      
    if (grepl(basename(path), pattern="CT_MA_ME_NH_RI_VT")) {
      state <- "CT,MA,ME,NH,RI,VT"
    } else if (grepl(basename(path), pattern="DE_MD_NJ")) {
      state <- "DE,MD,NJ,DC"
    } else if (grepl(basename(path), pattern="VA_WV")) {
      state <- "VA,WV"
    } else {
      state <- substr(basename(path), start=10, stop=11)
    }
    
    toretain <- cbind(AL17_user, AL17_producer) %>%
      dplyr::mutate(State = state, Year = year) %>%
      dplyr::select(Year, State, everything()) #%>%
      #dplyr::filter(!(is.na(Producer) | is.na(User))) # take out rows that do not have ground truth data OR CDL class was not represented in points to compare
    
    if (path == files[1] & year == 2012) {
      allstates <- toretain
    } else {
      allstates <- rbind(allstates, toretain)
    }
  }
}

# some states have combined accuracy assessments. Duplicate these rows and label with each state to facilitate joining with pixel freq data
towrite <- allstates %>%
  tibble() %>%
  transform(State = strsplit(State, ",")) %>%
  tidyr::unnest(State)

write.csv(towrite, './data/CDL_Accuracy/CDL_accuracy_long_allstates_2012to2020.csv', row.names = F)

```

# Load NVC contingency tables
```{r readnvc}
library(dplyr)

for (region in c('NC', 'NE', 'NW', 'SC', 'SE', 'SW')) {
  
  files <- list.files(paste0('./data/LANDFIRE_Accuracy/', region, '_Remap_Assessment_Package'), full.names = T)
  files <- files[grepl(files, pattern='.xlsx') & grepl(files, pattern='NVCGroup_Contingency') & !grepl(files, pattern='Original')] # specify contingency table
  
  path <- files

  # read correct sheet of excel file
  oneregion_agreement <- readxl::read_excel(path, sheet = "NVC Group", skip=1) %>%
  rename(`LANDFIRE EVT`= 1)
  
  oneregion_agreement <- dplyr::select(oneregion_agreement, -`Row Totals`, -`Percent Row Agreement`) %>%
    dplyr::rename(LANDFIRE_NVC=`LANDFIRE EVT`) %>%
    dplyr::filter(!LANDFIRE_NVC %in% c('Column Totals', 'Percent Column Agreement'))

  temp <- oneregion_agreement
  rownames(temp) <- temp$LANDFIRE_NVC
  temp <- temp[-1]

  temp <- mutate_all(temp, as.numeric)
  
  tab <- as.table(as.matrix(temp))
  dimnames(tab)[[1]] <- oneregion_agreement$LANDFIRE_NVC
  
  
  res <- greenbrown::AccuracyAssessment(tab)
  
  producer <- res[rownames(res) == 'ProducerAccuracy', !colnames(res) %in% c('Sum', 'UserAccuracy')]
  producer_nplots <- res[rownames(res) == 'Sum', !colnames(res) %in% c('Sum', 'UserAccuracy')]

  user <- res[!rownames(res) %in% c('Sum', 'ProducerAccuracy'), colnames(res) == 'UserAccuracy']
  user_nplots <- res[!rownames(res) %in% c('Sum', 'ProducerAccuracy'), colnames(res) == 'Sum']

  
  results_nvc <- data.frame(oneregion_agreement$LANDFIRE_NVC, Region = substr(basename(path), start=1, stop=2)) %>%
    dplyr::mutate(ProducerAccuracy = producer/100, ProducerNPlots_autokey=producer_nplots, UserAccuracy = user/100, UserNPlots_map=user_nplots) %>%
    dplyr::rename(LANDFIRE_NVC = oneregion_agreement.LANDFIRE_NVC) %>%
    dplyr::mutate(LANDFIRE_Class = substr(LANDFIRE_NVC, start=1, stop=4), LANDFIRE_Name = substr(LANDFIRE_NVC, start=6, stop=100)) %>%
    dplyr::select(LANDFIRE_NVC, LANDFIRE_Class, LANDFIRE_Name, everything())
  
  if (region == 'NC') {
    allregions_nvc <- results_nvc
  } else {
    allregions_nvc <- rbind(allregions_nvc, results_nvc)
  }
}


write.csv(allregions_nvc, './data/LANDFIRE_Accuracy/NVC_Accuracy_allregions.csv', row.names = F)
```

# Load EVT Contingency Tables
We need these because some NVC classes are directly mapped from EVT and NVC assessment skips these classes.

```{r readevt}
for (region in c('NC', 'NE', 'NW', 'SC', 'SE', 'SW')) {
  
  files <- list.files(paste0('./data/LANDFIRE_Accuracy/', region, '_Remap_Assessment_Package'), full.names = T)
  files <- files[grepl(files, pattern='.xlsx') & grepl(files, pattern='EcologicalSystems_Contingency') & !grepl(files, pattern='Original')] # specify contingency table
  
  path <- files

  # read correct sheet of excel file
  oneregion_agreement <- readxl::read_excel(path, sheet = "Ecological_Systems", skip=1) %>%
  rename(`LANDFIRE EVT`= 1)
  
  oneregion_agreement <- dplyr::select(oneregion_agreement, -`Row Totals`, -`Percent Row Agreement`) %>%
    dplyr::rename(LANDFIRE_EVT=`LANDFIRE EVT`) %>%
    dplyr::filter(!LANDFIRE_EVT %in% c('Column Totals', 'Percent Column Agreement'))

  temp <- oneregion_agreement
  rownames(temp) <- temp$LANDFIRE_EVT
  temp <- temp[-1]

  temp <- mutate_all(temp, as.numeric)
  
  tab <- as.table(as.matrix(temp))
  dimnames(tab)[[1]] <- oneregion_agreement$LANDFIRE_EVT
  
  
  res <- greenbrown::AccuracyAssessment(tab)
  
  producer <- res[rownames(res) == 'ProducerAccuracy', !colnames(res) %in% c('Sum', 'UserAccuracy')]
  producer_nplots <- res[rownames(res) == 'Sum', !colnames(res) %in% c('Sum', 'UserAccuracy')]

  user <- res[!rownames(res) %in% c('Sum', 'ProducerAccuracy'), colnames(res) == 'UserAccuracy']
  user_nplots <- res[!rownames(res) %in% c('Sum', 'ProducerAccuracy'), colnames(res) == 'Sum']

  
  results_evt <- data.frame(oneregion_agreement$LANDFIRE_EVT, Region = substr(basename(path), start=1, stop=2)) %>%
    dplyr::mutate(ProducerAccuracy = producer/100, ProducerNPlots_autokey=producer_nplots, UserAccuracy = user/100, UserNPlots_map=user_nplots) %>%
    dplyr::rename(LANDFIRE_EVT = oneregion_agreement.LANDFIRE_EVT) %>%
    dplyr::mutate(LANDFIRE_Class = substr(LANDFIRE_EVT, start=1, stop=4), LANDFIRE_Name = substr(LANDFIRE_EVT, start=6, stop=100)) %>%
    dplyr::select(LANDFIRE_EVT, LANDFIRE_Class, LANDFIRE_Name, everything())
  
  if (region == 'NC') {
    allregions_evt <- results_evt
  } else {
    allregions_evt <- rbind(allregions_evt, results_evt)
  }
}


write.csv(allregions_evt, './data/LANDFIRE_Accuracy/EVT_Accuracy_allregions.csv', row.names = F)
```

