---
title: "Decide which land cover layer is baseline"
author: "Melanie Kammerer"
date: "2/24/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = F, message = F)
```

## Objective
The goal of this script is to decide which land cover layer (CDL or NVC) is more accurate when compared with Chesapeake Conservancy high-resolution land cover. To determine this, I look at the pixels of CDL and NVC that disagree (e.g. CDL says pasture, NVC says forest) and extract Chesapeake land cover at these locations. 


## Specify which LANDFIRE vegetation map to use (EVT or NVC)
The two (main) options here are Existing Vegetation Type (LANDFIRE 1.0.5) or National Vegetation Classification (2.0).
```{r whichveglayer}
rm(list=ls())
veglayer <- 'nvc'
```

## Which land cover classes are in conflict?


```{r loaddata}
library(terra); library(dplyr); library(raster)
#load version of the combined map as an R data file (already has attribute table)
load(file=paste0('./data/CombinedVegCDLRasters/combined', veglayer, 'raster.RDA'))

evt <- raster::raster('D:/SpatialData/FingerLakesLandUse/LandFire_EVegType10.tif')
nvc <- raster::raster('D:/SpatialData/FingerLakesLandUse/LandFire_NatVegClassification.tif')
cdl <- raster::raster('D:/SpatialData/FingerLakesLandUse/USDA_CDL_2016_FingerLakes.tif')

evt2 <- terra::rast('D:/SpatialData/FingerLakesLandUse/LandFire_EVegType10.tif')
nvc2 <- terra::rast('D:/SpatialData/FingerLakesLandUse/LandFire_NatVegClassification.tif')
cdl2 <- terra::rast('D:/SpatialData/FingerLakesLandUse/USDA_CDL_2016_FingerLakes.tif')
combined2 <- terra::rast(paste0('./data/CombinedVegCDLRasters/Combined', toupper(veglayer), 'andCDL.tif'))

#load chesapeake layer for New York state
chesa <- terra::rast('D:/SpatialData/Chesapeake_Conservancy/_NY_STATEWIDE/_NY_STATEWIDE/NY_STATEWIDE.tif')

```
Now, we can identify which land cover classes in LANDFIRE and CDL disagree. I am particularly interested in the most common disagreements.

Make vector layer of centroids of all pixels that disagree
```{r disagreepixels}
taa <- terra::xyFromCell(combined2, cell=which(terra::values(combined2) == 0))
```

Extract original raster values for the pixels that disagree. Then, to summarize the most common CDL-NVC pairs (which land cover classes disagree), I convert raster values to a data frame.
```{r classdisagreement}
nvc_disagree <- terra::extract(nvc2, taa)
cdl_disagree <- raster::extract((cdl*-1), taa) #use raster package here bc terra isn't working for some unknown reason
chesa_disagree <- terra::extract(chesa, taa)

disagree <- data.frame(nvc_disagree[,1], cdl_disagree, chesa_disagree[,1])
names(disagree) <- c(toupper(veglayer), 'CDL', 'Chesapeake')

disagree <- dplyr::filter(disagree, !(CDL == 0 & NVC == 0)) %>%
  dplyr::mutate(LandCoverPair = paste0(NVC, "_", CDL)) 

```

## Summarize the most common CDL-LANDFIRE disagreements
```{r sumfreqency}
disagree_freq <- dplyr::group_by(disagree, NVC, CDL, Chesapeake, LandCoverPair) %>%
  dplyr::summarise(Freq= n()) %>%
  ungroup() %>%
  dplyr::mutate(Pct = Freq/sum(Freq), CDL=as.character(CDL), NVC=as.character(NVC))

#load tabular data for EVT
if (veglayer == 'evt') {
  vegclasses_key <- read.csv('D:/SpatialData/LandFire/US_105evt/CSV_Data/US_105evt_05262011.csv') %>%
    dplyr::mutate(VALUE = as.character(Value))
  name_column <- 'EVT_Name'; name_column <- sym(name_column)
} else if (veglayer == 'nvc') {
  vegclasses_key <- read.csv('D:/SpatialData/LandFire/US_200NVC/CSV_Data/LF_200NVC_05142020.csv') %>%
      dplyr::mutate(VALUE = as.character(VALUE))

  name_column <- 'NVC_Name'; name_column <- sym(name_column)
}

#read CDL class names
cdl_classes <- read.csv('D:/SpatialData/NASS_CDL/NASS_classes_simple.csv') %>% 
  dplyr::filter(VALUE < 500)  %>%#filter out CDL classes that I created for a different project
  dplyr::mutate(VALUE = as.character(-VALUE))

specify_decimal <- function(x, k) trimws(format(round(x, k), nsmall=k))

#Add land cover class names to frequency table
disagree_freq <- dplyr::left_join(disagree_freq, dplyr::select(cdl_classes, -GROUP), 
                   by=c('CDL' = 'VALUE')) %>%
  dplyr::rename(CDL_Class = CLASS_NAME) %>%
  dplyr::left_join(dplyr::select(vegclasses_key, VALUE, paste0(toupper(veglayer), '_Name')),
                   by=c('NVC' = 'VALUE')) %>%
    #take out land cover pairs that aren't actually in conflict
  dplyr::rename(NVC_Class = paste0(toupper(veglayer), '_Name')) %>%
  filter(!LandCoverPair %in% c('7908_-176', '7908_-1', '7908_-37','7933_-176', '7934_-37', '7934_-176',  '7974_-61', '7975_-61', '7977_-121','7977_-61', '9317_-176','9817_-37')) %>%
  dplyr::arrange(desc(Pct)) %>%
  dplyr::ungroup() %>%
  dplyr::mutate(Pct_rounded = specify_decimal(Pct, 4))

knitr::kable(dplyr::select(disagree_freq, -Pct, -Freq) %>% dplyr::filter(Pct_rounded > 0.01))

disagree_freq <- dplyr::select(disagree_freq, -Pct_rounded)

write.csv(disagree_freq, './data/CDL_NVC_PixelDisagree.csv')
```

```{r sumdisagree}

cdl_problemclasses <- dplyr::group_by(disagree_freq, CDL, CDL_Class) %>%
  dplyr::summarise(Pct = sum(Pct), Freq= sum(Freq)) %>%
  arrange(desc(Pct))
knitr::kable(dplyr::filter(cdl_problemclasses, Pct > 0.0011110))

nvc_problemclasses <- dplyr::group_by(disagree_freq, NVC, NVC_Class) %>%
  dplyr::summarise(Pct = sum(Pct), Freq= sum(Freq)) %>%
  arrange(desc(Pct))
knitr::kable(dplyr::filter(nvc_problemclasses, Pct > 0.0011110))

problem_pairs <- dplyr::group_by(disagree_freq, NVC_Class, CDL_Class, LandCoverPair) %>%
  dplyr::summarise(Pct = sum(Pct), Freq= sum(Freq)) %>%
  arrange(desc(Pct))
knitr::kable(dplyr::filter(problem_pairs, Pct > 0.0085089))

```

## Calculate CDL and NVC accuracy stats (compared with Chesapeake Land Cover)
Grass/pasture and other-hay non-alfalfa are a large percentage of the pixel disagreement (~71% of pixels). Is is suprisingly common for LANDFIRE and CDL to disagree on forest vs. grassland (trees vs. no trees). To determine which layer is more accurate, I compare against the Chesapeake high-resolution land cover. The Chesapeake layer does not have high thematic resolution (only a few classes), but it does differentiate low vegetation vs. trees.

```{r comparechesa, echo=F}
###### CDL compare against Chesapeake land cover
chesa_cdl_grass <- dplyr::filter(disagree_freq, CDL %in% c('-176', '-37'))
cdl_grass_agree <- sum(chesa_cdl_grass$Freq[chesa_cdl_grass$Chesapeake == '5'])

print(paste0('CDL grass: ', cdl_grass_agree/sum(chesa_cdl_grass$Freq[!is.na(chesa_cdl_grass$Chesapeake)])))


chesa_cdl_crops <- dplyr::filter(disagree_freq, CDL %in% c('-1', '-61', '-36', 
                                            '-5','-24', '-28', '-131', '-42', 
                                            '-58', '-27', '-49', '-205', '-21', '-12'))
cdl_crops_agree <- sum(chesa_cdl_crops$Freq[chesa_cdl_crops$Chesapeake == '5'])
print(paste0('CDL crops: ', cdl_crops_agree/sum(chesa_cdl_crops$Freq[!is.na(chesa_cdl_crops$Chesapeake)])))


chesa_cdl_forest <- dplyr::filter(disagree_freq, CDL %in% c('-141', '-142', '-143'))
cdl_forest_agree <- sum(chesa_cdl_forest$Freq[chesa_cdl_forest$Chesapeake %in% c('3', '10', '11', '12')])

print(paste0('CDL forest: ', cdl_forest_agree/sum(chesa_cdl_forest$Freq[!is.na(chesa_cdl_forest$Chesapeake)])))

print(paste0('CDL: ', (cdl_grass_agree + cdl_crops_agree + cdl_forest_agree) /     (sum(chesa_cdl_grass$Freq[!is.na(chesa_cdl_grass$Chesapeake)]) +
                                           sum(chesa_cdl_crops$Freq[!is.na(chesa_cdl_crops$Chesapeake)]) +
                                           sum(chesa_cdl_forest$Freq[!is.na(chesa_cdl_forest$Chesapeake)]))))

###### NVC compare against Chesapeake land cover
chesa_nvc_grass <- dplyr::filter(disagree_freq, NVC %in% c('7908', '7977', '7934', '9817',
                                                                 '6230', '7195'))
nvc_grass_agree <- sum(chesa_nvc_grass$Freq[chesa_nvc_grass$Chesapeake == '5'])

print(paste0('NVC grass: ', nvc_grass_agree/sum(chesa_nvc_grass$Freq[!is.na(chesa_nvc_grass$Chesapeake)])))

chesa_nvc_crops <- dplyr::filter(disagree_freq, NVC %in% c('7974', '7975', '7976', '7978', '6230'))
nvc_crops_agree <- sum(chesa_nvc_crops$Freq[chesa_nvc_crops$Chesapeake == '5'])

print(paste0('NVC crops: ', nvc_crops_agree/sum(chesa_nvc_crops$Freq[!is.na(chesa_nvc_crops$Chesapeake)])))


chesa_nvc_forest <- dplyr::filter(disagree_freq, NVC %in% c('6047', '7932', '9315', '6036', '9312', 
                                                            '6043', '7931', '7930', 
                                                            '6032', '6098', '7905', '6101'))
nvc_forest_agree <- sum(chesa_nvc_forest$Freq[chesa_nvc_forest$Chesapeake %in% c('3', '10', '11', '12')])

print(paste0('NVC forest: ',nvc_forest_agree/ sum(chesa_nvc_forest$Freq[!is.na(chesa_nvc_forest$Chesapeake)])))

print(paste0('NVC: ', (nvc_crops_agree + nvc_crops_agree + nvc_forest_agree) /(sum(chesa_nvc_grass$Freq[!is.na(chesa_nvc_grass$Chesapeake)]) + (sum(chesa_nvc_crops$Freq[!is.na(chesa_nvc_crops$Chesapeake)]) + sum(chesa_nvc_forest$Freq[!is.na(chesa_nvc_forest$Chesapeake)])))))
                                                                                                      
```

