---
title: "Calculate Accuracy of CDL and NVC rasters"
author: "Melanie Kammerer"
date: "1/11/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE)
```

## Objective
The goal of this script is to map the accuracy of CDL & NVC rasters. To do this, I use class-level data on spatial accuracy from USDA NASS and LANDFIRE for CDL and NVC, respectively. I combined accuracy statistics from two layers by calculating an area-weighted mean.

I start by loading accuracy data for EVT and NVC. We need NVC and EVT because NVC borrows some classes from EVT and LANDFIRE does not publish accuracy values for EVT classes in NVC data files. In this section I also create a list of LANDFIRE 'managed classes' (agriculture, burned, logged, etc). These classes were not included in reference database nor accuracy assessment so, when calculating data coverage, I exclude area covered in these classes.

```{r loadtabulardata, echo=F}
library(dplyr); library(logger); library(future); library(terra)
rm(list=ls())

CDLYear <- 2021

# load accuracy data from LANDFIRE and USDA NASS (aggregated & formatted in 'WrangleMergedAccuracyByCounty.Rmd' script)
evt <- read.csv('./data/LANDFIRE_Accuracy/EVT_Accuracy_allregions.csv')
nvc <- read.csv('./data/LANDFIRE_Accuracy/NVC_Accuracy_allregions.csv')

# accuracy assessment missing some classes (contingency tables sometimes only have classes with auto-key plots)

all_classes <- read.csv('./data/TabularData/LF_200NVC_05142020.csv')
toadd <- dplyr::filter(all_classes, !VALUE %in% nvc$LANDFIRE_Class) %>%
  dplyr::mutate(ProducerNPlots_autokey=0)

nvc <- dplyr::full_join(nvc, dplyr::select(toadd, VALUE, NVC_Name, ProducerNPlots_autokey), 
                        by=c('LANDFIRE_Class'='VALUE', 
                             'LANDFIRE_Name' ='NVC_Name','ProducerNPlots_autokey'))

length(unique(nvc$LANDFIRE_Class)) == length(unique(nvc$LANDFIRE_Name))
length(unique(nvc$LANDFIRE_Class)) == length(unique(all_classes$VALUE))


# custom max function that returns NA if both input values are NA
mymax <- function(...,def=NA,na.rm=FALSE) {
    if(!is.infinite(x<-suppressWarnings(max(...,na.rm=na.rm)))) {
      x } else {def}
}

# for NVC classes that were taken from EVT, use the accuracy data from EVT
lf <- dplyr::full_join(nvc, evt, by=c('LANDFIRE_Class','LANDFIRE_Name', 'Region'), suffix=c('.nvc', '.evt')) %>%
  dplyr::group_by(LANDFIRE_Class, LANDFIRE_Name, Region) %>%
  dplyr::mutate(ProducerAccuracy = mymax(ProducerAccuracy.nvc, ProducerAccuracy.evt, na.rm=T),
                ProducerNPlots_autokey = mymax(ProducerNPlots_autokey.nvc, ProducerNPlots_autokey.evt, na.rm=T),
                UserAccuracy = mymax(UserAccuracy.nvc, UserAccuracy.evt, na.rm=T),
                UserNPlots_map = mymax(UserNPlots_map.nvc, UserNPlots_map.evt, na.rm=T)) %>%
  dplyr::ungroup() %>%
  dplyr::mutate(LANDFIRE_NVC = paste(LANDFIRE_Class, LANDFIRE_Name))


# specify classes that COULD have plots in auto-key (are non-managed, not agriculture or NLCD developed)
nvc_agclasses <- c(7960:7999) # classes in LANDFIRE NVC that are agriculture

managed_classes <- lf$LANDFIRE_Class[grepl(lf$LANDFIRE_Name, pattern='Developed-') | 
                                       grepl(lf$LANDFIRE_Name, pattern='Recently Burned-') | 
                                       grepl(lf$LANDFIRE_Name, pattern='Recently Logged-') | 
                                       grepl(lf$LANDFIRE_Name, pattern='Recently Disturbed Other-') | 
                                       #grepl(lf$LANDFIRE_Name, pattern='Forest Plantation') | 
                                       lf$LANDFIRE_Class %in% nvc_agclasses |
                                         lf$LANDFIRE_Name == 'Open Water']
```
 
## Load NVC pixel frequency by county
Here, I load datasets generated by 'TabulatePixels3Rasters.R' script. All LANDFIRE accuracy assessments were conducted by region, so I also need to load a shapefile of the LF regions and label each county with the region it is contained within. Some counties cross regional boundaries, so I determine the appropriate region based on the centroid of each county polygons (some counties have multiple polygons due to non-contiguous land).
```{r loadfreq, echo=F}
library(dplyr)
# read county shapefile, remove polygons that are NA for county name (usually sections of water adjacent a state)
county_shp <- sf::st_read('./data/SpatialData/us_counties_better_coasts.shp') %>%
  dplyr::filter(!is.na(COUNTY))

# add NVC region to county shapefile
# load region shapefile and reproject to match counties
regions <- sf::st_read('./data/SpatialData/LANDFIRE/us_lf_zones/us_lf_zones.shp') %>%
  dplyr::group_by(LF2010_GA) %>%
  summarize(geometry = sf::st_union(geometry)) %>% # original region shapefile had multiple polygons per region, so I dissolve them
  sf::st_transform(crs = sf::st_crs(county_shp)) # project region polygon to match counties

plot(regions)

# convert county polygons to centroids and calculate intersection between regions and county centroids
la <- sf::st_centroid(county_shp) %>% 
  sf::st_join(regions, join=sf::st_intersects) %>%
  dplyr::rename(LF2010_Region=LF2010_GA) %>%
  sf::st_drop_geometry() %>%
  dplyr::select(FIPS, LF2010_Region) %>%
  dplyr::arrange(FIPS)

# add region column to original county shapefile
county <- dplyr::arrange(county_shp, FIPS) %>% cbind(la) %>%
  dplyr::group_by(FIPS, STATE, COUNTY, STATE_FIPS, LF2010_Region) %>%
  summarize(geometry = sf::st_combine(geometry)) %>%
  dplyr::ungroup() %>%
  dplyr::filter(!duplicated(paste0(STATE, COUNTY)))

#sf::st_write(county, './data/SpatialData/us_counties_better_coasts_LFregion.shp', append=F)

# read NVC pixel frequency data
nvc_county <- read.csv('./data/PixelFreq/NVC_CountyPixelFreq.csv') %>%
  dplyr::filter(!is.na(County)) %>%
  dplyr::group_by(State, County) %>%
  dplyr::mutate(PctCounty = (NCells/sum(NCells))*100) %>%
  dplyr::ungroup() 

# are there any counties in county shapefile that are NOT in dataset on NVC pixel frequency?
paste0(county$COUNTY, ", ", county$STATE)[!paste0(county$COUNTY, ", ", county$STATE) %in% paste0(nvc_county$County, ", ", nvc_county$State)]

nvc_county <- sf::st_drop_geometry(county) %>%
    dplyr::select(STATE, COUNTY, LF2010_Region) %>%
    dplyr::left_join(nvc_county, by=c('STATE'='State', 'COUNTY'='County'))

# how many classes in spatial data are missing from tabular data?
sort(unique(nvc_county$Class[!nvc_county$Class %in% lf$LANDFIRE_Class]))

# filter tabular data to ONLY classes in spatial data
lf2 <- dplyr::filter(lf, LANDFIRE_Class %in% nvc_county$Class)

# write clean version of tabular data
write.csv(lf, './data/NVC_Accuracy_allregions_cleaned.csv', row.names=F)

```

# Join NVC accuracy metrics with pixel frequency
```{r join_various_data}
# join accuracy values to pixel frequency data
nvc_accuracy <- dplyr::left_join(nvc_county, lf, by=c('Class'='LANDFIRE_Class', 'LF2010_Region'='Region')) %>%
  dplyr::select(-contains('.evt') , -contains('.nvc'))

# why are there some counties with NA for NVC value?
nvc_accuracy[is.na(nvc_accuracy$Class),]

# make new variable of reference database status (well-represented, poorly-represented, absent, or managed/ag)
nvc_accuracy$RFDB_Status <- if_else(nvc_accuracy$Class %in% managed_classes, 'absent, managed/ag/disturbed', 
                            if_else((nvc_accuracy$ProducerNPlots_autokey == 0|is.na(nvc_accuracy$ProducerNPlots_autokey)) & 
                                 !nvc_accuracy$Class %in% managed_classes,  'absent, could be added', 
                            if_else(nvc_accuracy$ProducerNPlots_autokey >= 30, 'well-represented',
                            if_else(nvc_accuracy$ProducerNPlots_autokey < 30 & nvc_accuracy$ProducerNPlots_autokey > 0, 'poorly-represented',
                                  'uh oh'))))


# calculate total number of cells per county as well as accuracy*NCells of a specific class (will sum in next step to get area-weighted average)
nvc_accuracy <- dplyr::group_by(nvc_accuracy, STATE, COUNTY) %>%
  dplyr::mutate(NCells_County= sum(NCells), Weight_ProdAcc = NCells*ProducerAccuracy,
                Weight_UserAcc = NCells*UserAccuracy)

# summarize ncell and accuracy by county and reference db status
# accuracy only applies to well-represented, but we will map data coverage of well and poorly represented classes
nvc_accuracy_bycounty <-  nvc_accuracy  %>%  
    dplyr::group_by(STATE, COUNTY, NCells_County, RFDB_Status) %>%
    dplyr::summarize(NCells_Group = sum(NCells, na.rm=T), 
    Weight_ProdAcc = sum(Weight_ProdAcc, na.rm=T)/NCells_Group,
    Weight_UserAcc = sum(Weight_UserAcc, na.rm=T)/NCells_Group, .groups='keep') %>%
  dplyr::mutate(RFDB_Status2=RFDB_Status) %>%
  dplyr::ungroup()

# reshape ncells to wide format
ncells <- tidyr::pivot_wider(nvc_accuracy_bycounty, id_cols=c(STATE:COUNTY, NCells_County), names_from=RFDB_Status, 
                     values_from=NCells_Group) %>%
  tidyr::replace_na(list(`well-represented` = 0, `poorly-represented` = 0))
  
# reshape accuracy to wide format, filter to only well-represented classes
acc <- dplyr::filter(nvc_accuracy_bycounty, RFDB_Status == 'well-represented') %>% 
  tidyr::pivot_wider(id_cols=c(STATE:COUNTY, NCells_County), names_from=RFDB_Status, 
                     values_from=c(Weight_ProdAcc, Weight_UserAcc)) %>%
  dplyr::rename(WtdUserAcc = `Weight_UserAcc_well-represented`, WtdProdAcc = `Weight_ProdAcc_well-represented`)

# translate ncells to percentage of un-managed area in each county
toplot <- dplyr::mutate(ncells, NCells_Unmanaged = (NCells_County - `absent, managed/ag/disturbed`),
                        Rep_PctUnmanaged = ((`well-represented` + `poorly-represented`)/NCells_Unmanaged)*100,
                        WellRep_PctUnmanaged = ((`well-represented`)/NCells_Unmanaged)*100)
```


## Wrangle CDL accuracy data
```{r wrangle_cdl}
names(county)

# load accuracy data
cdl <- read.csv('./data/CDL_Accuracy/CDL_accuracy_long_allstates_2012to2021.csv')
# filter cdl to selected year to match pixel freq data
cdl_oneyear <- dplyr::filter(cdl, Year %in% CDLYear)

# key to group CDL classes in arable or non-arable
cdl_classes <- read.csv('./data/TabularData/NASS_classes_pasture_is_arable.csv')
ag_in_cdl <- cdl_classes$VALUE[cdl_classes$GROUP == 'A']

# load frequency data
cdl_freq <- read.csv(paste0('./data/PixelFreq/CDL', CDLYear, '_CountyPixelFreq.csv'))

head(cdl_freq)
head(cdl_oneyear)

cdl_accuracy <- dplyr::left_join(cdl_freq, cdl_oneyear,  by=c('Class'='CDL_Class', 'State')) %>%
  dplyr::mutate(GT_Status = if_else(is.na(Producer), "no ground-truth", "present")) %>%
  dplyr::group_by(Year, State, County) %>%
  dplyr::mutate(NCells_County = sum(NCells)) %>%
  dplyr::filter(Class %in% ag_in_cdl) %>% # filter down to ONLY agricultural classes
  dplyr::mutate(NCells_Arable = sum(NCells), Weight_ProdAcc = NCells*Producer,
                Weight_UserAcc = NCells*User)

cdl_accuracy_bycounty <- cdl_accuracy  %>%
    dplyr::group_by(Year, State, County, NCells_County, NCells_Arable, GT_Status) %>% 
    dplyr::summarize(NCells_Group = sum(NCells, na.rm=T), 
    Weight_ProdAcc = sum(Weight_ProdAcc, na.rm=T)/NCells_Group,
    Weight_UserAcc = sum(Weight_UserAcc, na.rm=T)/NCells_Group, .groups='keep') %>%
  dplyr::mutate(GT_Status2=GT_Status) %>%
  dplyr::ungroup()

# reshape ncells to wide format
ncells_cdl <- tidyr::pivot_wider(cdl_accuracy_bycounty, id_cols=c(Year:County, NCells_County, NCells_Arable), names_from=GT_Status, 
                     values_from=NCells_Group) %>%
  tidyr::replace_na(list(`present` = 0, `no ground-truth` = 0)) %>%
  dplyr::mutate(PresentGT_PctArable = (`present`/NCells_Arable)*100, 
                CountyPctArable = (NCells_Arable/NCells_County)*100)
  
# reshape accuracy to wide format, filter to only well-represented classes
acc_cdl <- dplyr::filter(cdl_accuracy_bycounty, GT_Status == 'present') %>% 
  tidyr::pivot_wider(id_cols=c(Year:County, NCells_Arable), names_from=GT_Status, 
                     values_from=c(Weight_ProdAcc, Weight_UserAcc)) %>%
  dplyr::rename(WtdUserAcc = `Weight_UserAcc_present`, WtdProdAcc = `Weight_ProdAcc_present`)

```

## Make maps of NVC & CDL data coverage 
```{r bivariate_datacoverage, fig.width=7, fig.height=8}
library(classInt); library(ggplot2); library(viridis); library(dplyr)

# join results to spatial object for mapping
toplot_nvc <- dplyr::left_join(toplot, acc) %>%
  dplyr::left_join(acc) %>%
  dplyr::select(-starts_with('absent'), -contains('represented')) %>%
  dplyr::mutate(Dataset='Natural land', 
                Dataset_Name='NVC',
                FocalGroup_PctCounty=(NCells_Unmanaged/NCells_County)*100) %>%
  dplyr::mutate(WithData_PctFocalGroup=WellRep_PctUnmanaged,
                NCells_FocalGroup = NCells_Unmanaged) %>%
  dplyr::rename(State=STATE, County=COUNTY)                 

# join results to spatial object for mapping
toplot_cdl <- dplyr::left_join(acc_cdl, ncells_cdl) %>%
  dplyr::mutate(Dataset='Agricultural land', 
                Dataset_Name='CDL') %>%
  dplyr::mutate(FocalGroup_PctCounty=CountyPctArable, 
                WithData_PctFocalGroup=PresentGT_PctArable,
                NCells_FocalGroup=NCells_Arable) %>%
  dplyr::select(-Year)

# read data on merged accuracy calculated in 'WrangleMergedAccuracyByCounty.Rmd'
toplot_merged <- read.csv(paste0('./data/MergedAccuracy_', CDLYear, ".csv")) %>%
  dplyr::select(STATE, COUNTY, NCells_County, NCells_CDL, starts_with('Wtd'), well.represented) %>%
  dplyr::rename(County=COUNTY, State=STATE) %>%
  dplyr::mutate(Dataset='Natural + Agricultural land',
                Dataset_Name = 'NVC+CDL') %>%
  dplyr::left_join(dplyr::select(toplot_nvc, State, County, NCells_Unmanaged)) %>%
  dplyr::mutate(WithData_PctFocalGroup = (well.represented / (NCells_Unmanaged + NCells_CDL))*100, 
                FocalGroup_PctCounty = ((NCells_Unmanaged + NCells_CDL)/NCells_County)*100,
                NCells_FocalGroup = (NCells_Unmanaged + NCells_CDL)) %>%
  dplyr::select(-NCells_Unmanaged)

toplot_both <- dplyr::full_join(toplot_nvc, toplot_cdl) %>%
  dplyr::full_join(toplot_merged)

toplot_both <- dplyr::left_join(county, toplot_both, by = c('STATE'='State', 'COUNTY'='County'))

saveRDS(toplot_both, paste0('./data/TechnicalValidation/summarized_accuracy_data_CDL', CDLYear, '_NVC_Merged.rds'))
```

## Bi-variate choropleth map showing amount of agriculture and data coverage of NVC and CDL
First, I start with a bivariate choropleth map showing data coverage and the percent of each county in agriculture or natural land (for CDL and NVC,respectively). 
```{r bivariate}
# bi-variate choropleth map showing amount of agriculture and data coverage of NVC and CDL
library(biscale); library(ggplot2)

data <- dplyr::filter(toplot_both,  Dataset_Name != 'NVC+CDL') %>%
  bi_class(y=FocalGroup_PctCounty, x=WithData_PctFocalGroup, style='jenks', dim=3, keep_factors=T)

coverage_both <- ggplot() + geom_sf(data=data, mapping = aes(fill = bi_class), 
                                   color=NA, show.legend = FALSE) +
  #geom_sf(data=data, fill=NA, color='white', lwd=0.05) +
  bi_scale_fill(pal = "DkBlue", dim = 3)  +
  theme_classic(base_size=14) +
  theme(strip.text.x = element_text(size = 13),
        strip.text.y = element_text(size = 13)) +
  facet_wrap(~ Dataset_Name, ncol=1)

#coverage_both

legend_ag <- bi_legend(pal = "DkBlue",
                    dim = 3,
                    ylab = "% Agriculture ",
                    xlab = "Data Coverage ",
                    size = 10)+
          theme(plot.margin = margin(t = 0,  # Top margin
                             r = 0,  # Right margin
                             b = 0,  # Bottom margin
                             l = 0)) # Left margin

legend_nat <- bi_legend(pal = "DkBlue",
                    dim = 3,
                    ylab = "% Natural ",
                    xlab = "Data Coverage ",
                    size = 10)+
          theme(plot.margin = margin(t = 0,  # Top margin
                             r = 0,  # Right margin
                             b = 0,  # Bottom margin
                             l = 0)) # Left margin

library(cowplot); library(gridExtra)

finalPlot <- ggdraw() +
  draw_plot(coverage_both, 0, 0, 1, 1) +
  draw_plot(legend_ag, 0.8, .525, 0.14, 0.14) +
  draw_plot(legend_nat, 0.8, .05, 0.14, 0.14)

finalPlot

ggsave(plot=finalPlot, filename= paste0('./figures/DataCoverageInput_bivariate', CDLYear, '.pdf'),  width=7, height=8)
```

## Univariate map of data coverage. Are these easier to interpret?
```{r univariate_datacoverage,  fig.width=8.5, fig.height=10}

# maps of data coverage

natural.interval = BAMMtools::getJenksBreaks(toplot_both$WithData_PctFocalGroup, k = 7)
toplot_both$data.coverage.jenks = cut(toplot_both$WithData_PctFocalGroup, breaks=natural.interval, include.lowest = TRUE)

wellrep_map_jenks <- ggplot() + geom_sf(data=toplot_both, aes(fill=data.coverage.jenks),  color=NA) +
  guides(fill=guide_legend(title='Percent classes with\n ground-truth data')) +
  theme_classic(base_size=14) +
  theme(strip.text.x = element_text(size = 13),
      strip.text.y = element_text(size = 13)) +
  scale_fill_viridis(discrete=T, option='cividis') +
  facet_wrap(~Dataset_Name, ncol=1)
wellrep_map_jenks

ggsave(plot=wellrep_map_jenks, filename= paste0('./figures/DataCoverage3Panel_univariate', CDLYear, '.pdf'),  width=8.5, height=10)

```


## Make bivariate maps of NVC & CDL accuracy
```{r bivariate_accuracy, fig.width=14.5, fig.height=8}
toplot2_long <- dplyr::filter(toplot_both,  Dataset_Name != 'NVC+CDL') %>%
  dplyr::select(-starts_with('no'), -present) %>%
  tidyr::pivot_longer(cols=WtdProdAcc:WtdUserAcc, names_to='Accuracy_Type', values_to='Accuracy') %>%
  dplyr::mutate(`Accuracy_Type` = if_else(`Accuracy_Type` == 'WtdProdAcc', 'Producer Accuracy', 'User Accuracy'))


toplot_long <- toplot_both %>%
  dplyr::select(-starts_with('no'), -present) %>%
  tidyr::pivot_longer(cols=WtdProdAcc:WtdUserAcc, names_to='Accuracy_Type', values_to='Accuracy') %>%
  dplyr::mutate(`Accuracy_Type` = if_else(`Accuracy_Type` == 'WtdProdAcc', 'Producer Accuracy', 'User Accuracy'))

# bi-variate choropleth map showing amount of agriculture and accuracy of NVC and CDL

# producer accuracy
data_acc <- bi_class(toplot2_long, y=FocalGroup_PctCounty, x=Accuracy, style='jenks', dim=3, keep_factors=T)

acc_both <- ggplot() + geom_sf(data=data_acc, mapping = aes(fill = bi_class), 
                                   color=NA, show.legend = FALSE) +
  bi_scale_fill(pal = "DkCyan", dim = 3)  +
  theme_classic() +
  theme(strip.text.x = element_text(size = 13),
        strip.text.y = element_text(size = 13)) +
  facet_grid(Dataset_Name ~`Accuracy_Type`)

#coverage_both

legend_ag_user <- bi_legend(pal = "DkCyan",
                    dim = 3,
                    ylab = "% Agriculture ",
                    xlab = "User Accuracy ",
                    size = 10) +
          theme(plot.margin = margin(t = 0,  # Top margin
                             r = 0,  # Right margin
                             b = 0,  # Bottom margin
                             l = 0)) # Left margin

legend_nat_user <- bi_legend(pal = "DkCyan",
                    dim = 3,
                    ylab = "% Natural ",
                    xlab = "User Accuracy ",
                    size = 10) +
          theme(plot.margin = margin(t = 0,  # Top margin
                             r = 0,  # Right margin
                             b = 0,  # Bottom margin
                             l = 0)) # Left margin

legend_ag_prod <- bi_legend(pal = "DkCyan",
                    dim = 3,
                    ylab = "% Agriculture ",
                    xlab = "Producer Accuracy ",
                    size = 10) +
          theme(plot.margin = margin(t = 0,  # Top margin
                             r = 0,  # Right margin
                             b = 0,  # Bottom margin
                             l = 0)) # Left margin

legend_nat_prod <- bi_legend(pal = "DkCyan",
                    dim = 3,
                    ylab = "% Natural ",
                    xlab = "Producer Accuracy ",
                    size = 10) +
          theme(plot.margin = margin(t = 0,  # Top margin
                             r = 0,  # Right margin
                             b = 0,  # Bottom margin
                             l = 0)) # Left margin

library(cowplot); library(gridExtra)

finalPlot_acc <- ggdraw() +
  draw_plot(acc_both, 0, 0, 1, 1) +
  draw_plot(legend_ag_user, 0.85, .5, 0.14, 0.14) +
  draw_plot(legend_nat_user, 0.85, .05, 0.14, 0.14) +
  draw_plot(legend_ag_prod, 0.37, .5, 0.14, 0.14) +
  draw_plot(legend_nat_prod, 0.37, .05, 0.14, 0.14)

finalPlot_acc

ggsave(plot=finalPlot_acc, filename=paste0('./figures/AccuracyInput_bivariate', CDLYear, '.pdf'),  width=14.5, height=8)


toplot2_long %>% 
  dplyr::rename(Accuracy_Type =`Accuracy_Type`) %>%
  ggplot() +
  geom_point(aes(y=FocalGroup_PctCounty, x=Accuracy, color=Accuracy_Type)) +
  facet_wrap(~Dataset_Name+Accuracy_Type)
```

## Try univariate map of data coverage. Are these easier to interpret?
```{r univariate_accuracy, fig.width=15, fig.height=10}

# calculate jenk's breaks to use on map
natural.interval.accuracy <- BAMMtools::getJenksBreaks(toplot_long$Accuracy, k = 7)
toplot_long$accuracy.jenks = cut(toplot_long$Accuracy, breaks=natural.interval.accuracy , include.lowest = TRUE)

# map producer accuracy of NVC by county
accuracy_map_jenks <- ggplot() + geom_sf(data=toplot_long, aes(fill=accuracy.jenks),  color=NA) +  
  guides(fill=guide_legend(title='Accuracy \n(area-weighted)')) +
  theme_classic(base_size=14) +
  scale_fill_viridis(discrete=T, option='inferno') +
  facet_grid(Dataset_Name ~`Accuracy_Type`) +
  theme(strip.text.x = element_text(size = 14),
        strip.text.y = element_text(size = 14))

accuracy_map_jenks

ggsave(plot=accuracy_map_jenks, filename=paste0('./figures/Accuracy3panel_univariate', CDLYear, '.pdf'), width=15, height=10)

```
