---
title: "Plot Example of Merged Rasters"
author: "Melanie Kammerer"
date: "1/6/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Objective
The goal of this script is to create a figure showing the input, intermediate, and output rasters associated with CDL-NVC merge workflow. I'm using small rasters created in MakeExampleSmallRasters.R script. The example raster happens to be in the Finger Lakes region.

## Load data
```{r loadrasters}
rm(list=ls())
library(raster); library(dplyr)

# load function to plot categorical maps
source('./code/functions/plot_categorical_raster.R')
# load function to adjust margin settings in levelplot
source('./code/functions/noMargins.R')


cdl <- raster::raster('./data/SpatialData/ExampleSmallRasters/small_cdl.tif')
nvc <- raster::raster('./data/SpatialData/ExampleSmallRasters/small_nvc.tif')
merged_wgaps <- raster::raster('./data/SpatialData/ExampleSmallRasters/merged_with_gaps.tif') %>%
  abs()
merged_nogaps <- raster::raster('./data/SpatialData/ExampleSmallRasters/merged_gapsfilled.tif') %>%
  abs()
```

Load tabular data of class names to label maps
```{r loadtabulardata}
nvc_classes <- read.csv('./data/TabularData/LF_200NVC_05142020.csv') %>%
    dplyr::mutate(VALUE = as.character(VALUE)) %>%
    dplyr::filter(VALUE %in% raster::values(nvc))

# read CDL class names
cdl_classes <- read.csv('./data/TabularData/NASS_classes_pasture_is_arable.csv') %>% 
  dplyr::filter(VALUE < 500) %>% #filter out CDL classes that I created for a different project
  dplyr::filter(VALUE %in% raster::values(cdl))

merged_attribute_table <- read.csv('./data/TabularData/CombinedRasterAttributeTable_CDLNVC.csv') %>%
  dplyr::mutate(VALUE = abs(VALUE))
```

```{r makemaps, fig.width=9, fig.height=7}
library(rasterVis); library(raster); library(svglite)

##### PLOT CDL

cdl_map <- plot_categorical_raster(map=cdl, attribute_table=cdl_classes)
cdl_map

cdl_wlegend <- plot_categorical_raster(map=cdl, attribute_table=cdl_classes, draw_legend=T)
cdl_wlegend

##### PLOT NVC

nvc_map <- plot_categorical_raster(map=nvc, attribute_table=nvc_classes)
nvc_map


nvc_wlegend <- plot_categorical_raster(map=nvc, attribute_table=nvc_classes, draw_legend=T)
nvc_wlegend

# save small rasters with correct colors
svglite('./figures/ExampleRasterMaps/ExampleRaster_CDL.svg', width=4.111, height=4.625)

print(
 cdl_map
)
dev.off()

# save small rasters with correct colors
svglite('./figures/ExampleRasterMaps/ExampleRaster_CDL_wlegend.svg', width=4.75, height=4.625)

print(
 cdl_wlegend
)
dev.off()


svglite('./figures/ExampleRasterMaps/ExampleRaster_NVC.svg', width=4.111, height=4.625)

print(
 nvc_map
)
dev.off()

svglite('./figures/ExampleRasterMaps/ExampleRaster_NVC_wlegend.svg', width=9, height=7)

print(
 nvc_wlegend
)
dev.off()


svglite::svglite('./figures/ExampleRasterMaps/ExampleRaster_ForScalebar.svg', width=4.111, height=4.625)

plot(nvc)
raster::scalebar(750, type='bar', divs=4, below='meters', adj=c(0.5, -1.25))
prettymapr::addnortharrow()

dev.off()

```

## Plot derived spatial products
```{r outputmaps, fig.width=9, fig.height=7}
library(dplyr)

# filter down to classes contained in merged raster layers
all_classes <- dplyr::arrange(merged_attribute_table, VALUE)

merged_wgaps_classes <- dplyr::filter(all_classes, VALUE %in% raster::values(merged_wgaps))
merged_nogaps_classes <- dplyr::filter(all_classes, VALUE %in% raster::values(merged_nogaps))

##### Plot merged map, with gaps (output from step 1 of geospatial workflow)

merged_wgaps_map <- plot_categorical_raster(map=merged_wgaps, attribute_table=merged_wgaps_classes)
merged_wgaps_map

##### Plot merged map, without gaps (output from step 2 of geospatial workflow)

merged_nogaps_map <- plot_categorical_raster(map=merged_nogaps, attribute_table=merged_nogaps_classes)
merged_nogaps_map

merged_nogaps_map_wlegend <- plot_categorical_raster(map=merged_nogaps, attribute_table=merged_nogaps_classes, draw_legend=T)
merged_nogaps_map_wlegend

library(svglite)
svglite('./figures/ExampleRasterMaps/ExampleRaster_Merged_OutputStep1.svg', width=4.111, height=4.625)

print(
  merged_wgaps_map
)
dev.off()

svglite('./figures/ExampleRasterMaps/ExampleRaster_Merged_OutputStep2.svg', width=4.111, height=4.625)

print(
  merged_nogaps_map
)
dev.off()


```


```{r arrangemaps, fig.height=11.5, fig.width=9}
library(gridExtra); library(cowplot)
# from github:
devtools::install_github("delta-rho/datadr")
devtools::install_github("delta-rho/trelliscope")

library(trelliscope)
#grid.arrange(cdl_map, nvc_map, ncol=1, heights=c(1,1.1))


svglite('./figures/ExampleRasterMaps/ExampleRaster_CDL_NVC_Merged.svg', width=9, height=20)

print(
  plot_grid(cdl_map, nvc_map, merged_wgaps_map, merged_nogaps_map, align="v", nrow=4) #, rel_widths=c(1,1.1))
)
dev.off()

```

## Binary versions of all maps
```{r binary}
nvc_agclasses <- c(7960:7999) # classes in LANDFIRE NVC that are agriculture
cdl_agclasses <- cdl_classes$VALUE[cdl_classes$GROUP == 'A']

cdl_bin <- cdl %in% cdl_agclasses
nvc_bin <- nvc %in% nvc_agclasses

cdl_bin_t <- ratify(cdl_bin)
rat <- levels(cdl_bin_t)[[1]]
rat$CLASS_NAME <- c("Not agriculture", "Agriculture")

bin_theme <- rasterTheme(c('#565656', '#CFCFCF'))

cdlbin_map <- rasterVis::levelplot(cdl_bin, par.settings= noMargins(bin_theme, rightkey=T),
                               margin=list(draw=F), 
                               scales=list(draw=F))
cdlbin_map

nvcbin_map <- rasterVis::levelplot(nvc_bin, par.settings= noMargins(bin_theme, rightkey=T),
                               margin=list(draw=F), 
                               scales=list(draw=F))
nvcbin_map

# merged raster with gaps
merged_wgaps_bin <- raster::reclassify(merged_wgaps, rcl=data.frame(is=1001, becomes=NA))# reclassify unresolved conflict as NA so it shows up on binary raster
merged_wgaps_bin[merged_wgaps_bin %in% cdl_agclasses & !is.na(merged_wgaps_bin)] <- 1
merged_wgaps_bin[!(merged_wgaps %in% cdl_agclasses) & !is.na(merged_wgaps_bin)] <- 0

# merged raster no gaps
merged_nogaps_bin <- raster::reclassify(merged_nogaps, rcl=data.frame(is=1001, becomes=NA))# reclassify unresolved conflict as NA so it shows up on binary raster
merged_nogaps_bin[merged_nogaps_bin %in% cdl_agclasses & !is.na(merged_nogaps_bin)] <- 1 #a different way to reclassify a raster
merged_nogaps_bin[!(merged_nogaps %in% cdl_agclasses) & !is.na(merged_nogaps_bin)] <- 0


merged_wgaps_bin_t <- ratify(merged_wgaps_bin)
rat <- levels(merged_wgaps_bin_t)[[1]]
rat$CLASS_NAME <- c("Not agriculture", "Agriculture")

bin_theme <- rasterTheme(c('#565656', '#CFCFCF'))

merged_wgapsbin_map <- rasterVis::levelplot(merged_wgaps_bin, par.settings= noMargins(bin_theme, rightkey=T),
                               margin=list(draw=F), 
                               scales=list(draw=F))
merged_wgapsbin_map

merged_nogapsbin_map <- rasterVis::levelplot(merged_nogaps_bin, par.settings= noMargins(bin_theme, rightkey=T),
                               margin=list(draw=F), 
                               scales=list(draw=F))
merged_nogapsbin_map
```



```{r arrangemaps2, fig.height=11.5, fig.width=9}
library(gridExtra); library(cowplot); library(svglite)
# from github:
devtools::install_github("delta-rho/datadr")
devtools::install_github("delta-rho/trelliscope")


svglite('./figures/ExampleRasterMaps/ExampleRaster_CDL_NVC_Merged_Binary.svg', width=9, height=20)

print(
  plot_grid(cdlbin_map, nvcbin_map, merged_wgapsbin_map, merged_nogapsbin_map, align="v", nrow=4) #, rel_widths=c(1,1.1))
)
dev.off()



# save single binary maps
svglite('./figures/ExampleRasterMaps/ExampleRaster_CDL_Binary.svg', width=4.111, height=4.625)

print(
   cdlbin_map
)
dev.off()

svglite('./figures/ExampleRasterMaps/ExampleRaster_NVC_Binary.svg', width=4.111, height=4.625)

print(
  nvcbin_map
)
dev.off()

svglite('./figures/ExampleRasterMaps/ExampleRaster_Merged_OutputStep1_Binary.svg', width=4.111, height=4.625)

print(
   merged_wgapsbin_map
)
dev.off()

svglite('./figures/ExampleRasterMaps/ExampleRaster_Merged_OutputStep2_Binary.svg', width=4.111, height=4.625)

print(
  merged_nogapsbin_map
)
dev.off()


```

